### 2021-05-09 papers/SYRCoSE/response.txt

> Unfortunately, the Event Structure (ES) of Fig2 does not correspond exactly to the set of executions of Fig1: Fig1 suggests that the read operation is carried out after all write actions; this cannot be concluded from the ES of Fig2.

> Fig 9: the prime event structure forgets the difference between the green and the black preorder, therefore it does not express the requirement that in order R(x,2) to occur it must be "immediately preceded" by W(x,2) (in the sense "last write of x before the read"). If you consider this as a prime event structure an execution W(x,2) . W(x,1) . R(x,2) is not forbidden, as W(1,x) and W(2,x) are independent

We answer both of this questions below, as they are connected to each other.

The requirement that the "read is preceded by the last write to the same location" 
in fact corresponds to the sequentially consistent memory model. 
In other models (e.g. total store order TSO, or release/acquire RA) this condition is relaxed
(these models do not require an existence of total order on all events within a single execution (configuration)
and thus in general there is no unique "last" write to read-from).

@@

Our construction of event structure guarantees only the basic condition --- 
acyclicity of program order and reads from. It is, however, a necessary 
precondition for a wide class of memory models, including sequential consistency,
total store order, release/acquire, etc.

Whenever the configuration is extracted from the event structure
it can be checked to additionally satisfy the consistency predicate 
of a particular memory model 
(we briefly mention this in the paper, at the end of Section V).

### 2021-05-09 papers/SYRCoSE/response.txt

Whenever the configuration is extracted from the event structure
it can be checked to additionally satisfy the consistency predicate 
of a particular memory model 
(we briefly mention this in the paper, at the end of Section V).

Moreover, a po+rf acyclic prime event structure together with 
a consistency predicate for a particular memory model 
can be seen as a prime event structure with general (non-binary) conflict. 
In other words, a consistency predicate induces another notion of the conflict.
We are currently working on the theory of prime event structures with 
general conflict that would give us a more solid theoretical background 
for expressing various memory consistency models in the framework of event structures.

As for Fig.1 and Fig.2, you are right here. 
Fig.1. corresponds to sequentially consistent executions of the program,
but the Fig.2 presents po+rf acyclic event structure.
We will try to address this problem and remove the confusion.

> A bit more information about the Coq libraries you use, and why yo use them would be welcome. 
> There is space to say a bit more on the approach, may be also for those not "fluent in Coq".
> The library is not presented at all, only the application. One would like to get some information about the library itself

### 2021-05-10 papers/SYRCoSE/overview.tex
overview: add more on mathcomp

\section{Overview}

@@

We build our mechanisation on top of the \mathcomp~\cite{Mahboubi-Tassi:MATHCOMP17} library 
using the \ssreflect~\cite{Gonthier-al:SSR2016} extension of the \coq system.
We also use the \emph{small-scale reflection} 
methodology~\cite{Gonthier-Assia:SSR2010, Gonthier-al:SSR2016}, 
a key ingredient of \ssreflect.

@@

To achieve better automation and e.g. get \emph{proof irrelevance}
automatically, one is encouraged
to use \emph{decision} procedures whenever possible.
For example, in the context of our library, 
we encode the binary relations of the event structures
as decidable \texttt{bool}-valued relations, 
\ie $\caOrd, \cfRel : E \fun E \fun \texttt{bool}$,
as opposed to \emph{propositional} 
relations of type $E \fun E \fun \texttt{Prop}$.

>>>>

\section{Overview of Our Library}

@@

We build our mechanisation on top of the \mathcomp~\cite{Mahboubi-Tassi:MATHCOMP17} library 
which is an extensive and coherent repository of formalized mathematical theories,
whose implementation is based on the \ssreflect~\cite{Gonthier-al:SSR2016} extension of the \coq system.
By using \mathcomp, we draw on the large corpus of already formalised algorithms and mathematical results:
its core modules feature support for a range of useful data structures,
e.g. numbers, sequences, finite graphs,
and also interfaces: types with decidable equality, subtypes, finite types, and so on.

We also use the \emph{small-scale reflection} 
methodology~\cite{Gonthier-Assia:SSR2010, Gonthier-al:SSR2016}, 
a key ingredient of \ssreflect.

@@

To achieve better automation and e.g. get \emph{proof irrelevance}
for free, one is encouraged
to use \emph{decision} procedures whenever possible.
For example, in the context of our library, 
we encode the binary relations of the event structures
as decidable \texttt{bool}-valued relations, 
\ie $\caOrd, \cfRel : E \fun E \fun \texttt{bool}$,
as opposed to \emph{propositional} 
relations of type $E \fun E \fun \texttt{Prop}$.
